\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\definecolor{linkblue}{RGB}{25,103,210}
\hypersetup{colorlinks=true,linkcolor=linkblue,urlcolor=linkblue,bookmarksopen=true}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage[T1]{fontenc}
% \usepackage{newtxtext,newtxmath} % Times-like font compatible with pdfLaTeX

\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\newcommand{\fancysection}[1]{%
  \vspace{.5em}
  \noindent
  \makebox[\linewidth]{%
    \leavevmode
    \leaders\hrule height 0.4pt\hfill
    \hspace{0.8em}
    \textbf{#1}
    \hspace{0.8em}
    \leaders\hrule height 0.4pt\hfill
  }%
  \vspace{.2em}
}
\setlist[itemize]{noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, left=0.5cm}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE \textbf{Mohamed Fathy Salah} | Backend Engineer}\\[0.5em]
  \href{mailto:mohamedfathy29908@gmail.com}{mohamedfathy29908@gmail.com}
  \quad +20 114 319 1824
  \quad Cairo, Egypt \\[0.2em]
  \href{https://portfolio.mohamedfathy29908.workers.dev/}{portfolio} \quad
  \href{https://linkedin.com/in/mohamed-fathy-b30047202}{linkedin}\quad
  \href{https://github.com/Mohamed-Fathy-Salah}{GitHub} \quad
  \href{https://leetcode.com/u/user1869Z/}{LeetCode} \quad
\end{center}
\vspace{-1em}

\fancysection{Experience}
\begin{itemize}[left=0pt]
  \item \textbf{BackEnd Engineer, Luciq} \hfill Feb 2026 -- Present \\
    \textit{Tech Stack: go}
    \vspace{.1em}
  \item \textbf{BackEnd Engineer, EFG Holding}
    \hfill (1 year 11 months) Apr 2024 -- Feb 2026 \\
    \textit{Maintained and enhanced 17 microservices with a strong
      focus on performance, scalability, security, and
      consistency.\\Tech Stack: .NET, SQL Server, MongoDB, Redis,
    RabbitMQ, Python, Microservices, Clean and Layered Architecture}

    \begin{itemize}[left=0pt]
      \item \textbf{Payment Service Optimization:}
        Reduced execution time by:
        \begin{itemize}
          \item Resolving a race condition caused by concurrent row inserts.
          \item Parallelizing client payments for improved throughput.
          \item Optimizing algorithm complexity to \texttt{O(n log n)}.
          \item Limiting database interactions to two trips: one for
            read and one for update.
        \end{itemize}

      \item \textbf{Rule Engine Optimization (ValU):}
        Improved execution time by 350% by:
        \begin{itemize}
          \item Precompiling rules, keys, and formulas.
          \item Using lazy evaluation for conditional logic.
          \item Replacing multiple key resolutions with a single
            compiled execution path.
          \item Optimizing rule definitions, keys, and stored procedures.
          \item Vertically slicing large tables to isolate
            infrequently used columns.
          \item Rewrote the entire service by separating business
            logic into .NET code and moving dynamic configurations to
            the database, reducing the 95th percentile execution time
            from 70 seconds to 2 seconds.
        \end{itemize}

      \item \textbf{Distributed Transactions:}
        Implemented the Saga Pattern for consistent distributed
        transaction management across services.

      \item \textbf{Database Optimization:}
        \begin{itemize}
          \item Replaced inefficient N+1 queries with optimized
            single-query operations.
          \item Added Redis caching to reduce DB load and response times.
          \item Created targeted indexes and applied table slicing to
            enhance performance.
          \item Cut database load by 70\% and reduced API response time by 40\%.
        \end{itemize}

      \item \textbf{Data \& Workflow Migration:}
        \begin{itemize}
          \item Automated the migration of old Elsa workflows.
          \item Transformed 100,000+ unstructured records from Excel
            and Word documents into structured relational data prior to go-live.
        \end{itemize}

      \item \textbf{Team Contributions:}
        \begin{itemize}
          \item Led code reviews and enforced best practices.
          \item Mentored junior developers on architecture and coding standards.
          \item Applied OWASP-aligned security practices across services.
          \item Authored internal scripts to automate repetitive
            daily tasks, improving team efficiency and consistency.
        \end{itemize}
    \end{itemize}

\end{itemize}
\vspace{0em}

\fancysection{Skills}
\begin{itemize}[left=0pt]
  \item \textbf{Programming Languages:} C\# (Proficient), C++,
    JavaScript, TypeScript, Python.
  \item \textbf{.NET Ecosystem:} .NET, ASP.NET Core, Entity Framework
    Core, Dapper ORM, LINQ, MassTransit, SignalR, xUnit, Moq.
  \item \textbf{Web \& API Development:} RESTful APIs, HTTP,
    WebSockets, gRPC, GraphQL, HTML, CSS.
  \item \textbf{Databases:} SQL, SQL Server, PostgreSQL, SQLite, MongoDB, Redis.
  \item \textbf{Message Brokers \& Eventing:} RabbitMQ, MassTransit,
    Event-Driven Architecture, Pub/Sub Messaging.
  \item \textbf{Architecture \& Design:} Microservices, Modular
    Monolith, Layered, Hexagonal, Onion, Clean Architecture, SOLID
    Principles, Design Patterns, Test Pyramid, Object-Oriented
    Programming (OOP).
  \item \textbf{DevOps \& CI/CD:} Git, GitHub, GitHub Actions,
    Docker, Kubernetes, OpenShift, Azure DevOps.
  \item \textbf{Linux \& Scripting:} Bash scripting, systemd, Linux
    development environment.
  \item \textbf{Computer Science Foundations:} Algorithms, Data
    Structures, Race Condition Debugging, Caching Strategies.
  \item \textbf{Security:} Familiarity with OWASP best practices for
    secure software development.
  \item \textbf{Soft Skills:} Communication with stakeholders, Team
    collaboration and mentoring, Rapid adaptability, Problem-solving,
    Critical thinking, Effective time management.
  \item \textbf{Languages:} Arabic (Native), English (Proficient - C2).
\end{itemize}
\vspace{0em}

\fancysection{Projects}
\begin{itemize}[left=0pt]
  \item \textbf{\href{https://maskan.site}{Maskan}} \textit{.NET,
    C\#, PostgreSQL, ReactJS, Tailwind, AWS EC2, CICD, Contabo VPS} \\
    Multi-tenant real estate management web application for brokers,
    featuring role-based access control, browser caching strategies,
    CDN integration, and compliance with OWASP security best
    practices; supports 5,000+ unique visitors per month and includes
    real-time user notifications for matching property requests.
  \item \textbf{\href{https://circle0.netlify.app}{Circle}}
    \textit{TypeScript, React Native, Sqlite, Expo} \\
    cross-platform expense management application for
    personal-external-group expenses-incomes-transfers, featuring an
    optimized algorithm for minimal settlement plans.
  \item \textbf{E-Commerce VTON} \textit{TypeScript, Express, Python,
      FastAPI, Machine Learning, 3D Modeling, MongoDB, Next.js, NATS,
    Kubernetes, CI/CD} \\
    Event-driven microservice platform for virtual garment shopping.
    \vspace{.5em}
  \item \textbf{Healthy Meal} \textit{TypeScript, Apollo GraphQL,
    PostgreSQL, OAuth, Jest, CI/CD} \\
    Meal planning system based on preferences, ingredients, and body shape.
\end{itemize}
\vspace{0em}

\fancysection{Education}
\begin{itemize}[left=0pt]

  \item \textbf{Benha University} \hfill B.Eng. in Computer
    Engineering (GPA: 4.0 / 91\%) \hfill Sep 2017 -- Jun 2022
\end{itemize}

\vspace{0em}

\fancysection{Awards}
\begin{itemize}[left=0pt]
  \item Ranked 1st in Bachelor (2022)
  \item Ranked 118th in ECPC Qualification (2021)
  \item Ranked 21st in ECPC Qualification and 30th in ACPC Qualification (2022)
  \item \href{https://cert.efset.org/8qM58k}{EF SET Certificate}
\end{itemize}
\vspace{0em}

\fancysection{Courses \& Books}
\begin{itemize}[left=0pt]
  \item \textbf{.NET 8 Microservices}: ASP.NET Web API, Docker,
    RabbitMQ, gRPC, YARP Gateway
  \item \textbf{Network Engineering}: Low latency and high throughput
    backend design
  \item \textbf{Node.js + React Microservices}: E-Commerce microservice app
  \item \textbf{Database Systems (CMU)} | \textbf{Performance Engineering (MIT)}
  \item Clean Code | Code Refactoring | Design Patterns | DS \& Algo Made Easy
  \item
    \href{https://github.com/ashishps1/awesome-low-level-design}{\textbf{Awesome
    Low Level Design}} |
    \href{https://github.com/ashishps1/awesome-system-design-resources}{\textbf{Awesome
    System Design}}
\end{itemize}
\vspace{0em}

\end{document}
